---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# exoplanets

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/tyluRp/exoplanets.svg?branch=master)](https://travis-ci.org/tyluRp/exoplanets)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/tyluRp/exoplanets?branch=master&svg=true)](https://ci.appveyor.com/project/tyluRp/exoplanets)
[![Codecov test coverage](https://codecov.io/gh/tyluRp/exoplanets/branch/master/graph/badge.svg)](https://codecov.io/gh/tyluRp/exoplanets?branch=master)
<!-- badges: end -->

The goal of exoplanets is to provide access to [NASA's Exoplanet Archive](https://exoplanetarchive.ipac.caltech.edu/index.html) database in R. The functionality of this package is very minimal and is simply an R interface to access exoplanet data in the following ways:

* By providing a table name
* By providing a query URL

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("tylurp/exoplanets")
```

## Example

This is a basic example which shows you how to access data from the exoplanet table:

```{r example}
library(exoplanets)
library(tibble)

exoplanets <- exo()

as_tibble(exoplanets)
```

To access data from a different table you can use the table parameter:

```{r}
keplernames <- exo(table = "keplernames")

as_tibble(keplernames)
```

To get a list of all available tables:

```{r}
names(tbls) 
```

Finally, you can take a look at the [docs](https://exoplanetarchive.ipac.caltech.edu/docs/program_interfaces.html) and use `eco_raw` to write out queries in their entirety. Spaces and single quotes will be escaped automatically. The only supported format is CSV so do not request JSON, ipec, or others:

```{r}
exoplanets2 <- exo_raw("https://exoplanetarchive.ipac.caltech.edu/cgi-bin/nstedAPI/nph-nstedAPI?table=exoplanets")

as_tibble(exoplanets2)
```
