---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The exoplanets package lets users access [NASA's Exoplanet Archive](https://exoplanetarchive.ipac.caltech.edu/index.html) database in two ways:

1. By providing a table name using `exo()`
2. By providing a query URL using `exo_raw()`

Where `exo()` simply requires the name of a table and `exo_raw()` requires the full, raw URL. For example, the following lines are equivalent:

```{r setup}
library(exoplanets)

exoplanets1 <- exo("exoplanets")
exoplanets2 <- exo_raw("https://exoplanetarchive.ipac.caltech.edu/cgi-bin/nstedAPI/nph-nstedAPI?table=exoplanets")

all.equal(exoplanets1, exoplanets2)
```

To see a list of all available tables see the documentation [here](https://exoplanetarchive.ipac.caltech.edu/docs/program_interfaces.html). Additionally, a list `exo_tables` is available:

```{r exo_tables}
names(exo_tables)
```

If using RStudio, this list allows convenient autocompletion in case you forget the table names:

```{r exo_tables autocomplete}
k2names <- exo(exo_tables$k2names)
str(k2names)
```

Finally, there are 3 tables which require an additional parameter in order to access them, these are all time series datasets:

```{r exo_table time series}
names(exo_tables)[which(grepl("timeseries", names(exo_tables)))]
```

For example, the `kelttimeseries` table requires either the quarter or a Kepler ID, `exo("kelttimeseries&quarter=14")`. Note, these datasets are quite large and can take awhile. All of these additional parameter requirements are documented in the [documentation](https://exoplanetarchive.ipac.caltech.edu/docs/program_interfaces.html).



