---
title: "Introduction to exoplanets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction-to-exoplanets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(exoplanets)
formals(exo)$progress <- FALSE
formals(exo_raw)$progress <- FALSE
formals(exo_column_names)$progress <- FALSE
formals(exo_wasp)$progress <- FALSE
```

# Introduction

The exoplanet package is a minimal interface to the [NASA Exoplanet Archive](https://exoplanetarchive.ipac.caltech.edu/index.html). The goal is to make it as easy as possible to interact with the API from R. Some key features are:

1. `exo`: the main function for pulling data from the API via table names
2. `exo_kelt`, `exo_kepler`, and `exo_wasp`: the functions for pulling time series data
3. `exo_summary`: a function for summarising the database

# Data Access

By default, `exo` will pull from the exoplanets table.

```{r setup}
library(exoplanets)

df_exo <- exo()
df_exo
```

If you want to explore other datasets, take a look at `exo_tables` a list that contains all available data. One nice feature of having a list of available data is that we can utilize autocompletion (assuming you're using RStudio). Autocompletion paired with `exo` is an easy solution to pull whatever data you're interested in, no need to memorize the table name.

```{r}
# available data
str(exo_tables)

# using exo_tables with exo
df_stars <- exo(exo_tables$missionstars)
df_stars
```

# Time Series Data Access

There is one caveat to `exo`, it is not equiped to handle some of the available datasets, specifically time series datasets. This is because time series datasets are very large and require additional parameters to narrow in on a subset of the data.

Instead of cramming additional functionality into `exo`, 3 functions have been added specifically for time series data, they are: 

1. `exo_kelt`: for the `kelttimeseries` table
2. `exo_kepler`: for the `keplertimeseries` table
3. `exo_wasp`: for the `superwasptimeseries` table

```{r}
df_wasp <- exo_wasp(sourceid = "1SWASP J191645.46+474912.3")
df_wasp
```

